---
title: "Homework6"
author: "Kunaal Raghav"
format: pdf
editor: visual
---

## Install Packages

```{r}
#install.packages("bootstrap")
library(bootstrap)
library(MASS)
```

## Question 1: Bases and Sopranos

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

Part B

```{r}

#Data creation
x <- c(102,115,127,127,162,180,184,205,239,240)


theta_hat <- min(x)

#LOOCV Calculation
theta_i <- sapply(1:length(x), function(i) min(x[-i]))

#Equation
theta_jack <- length(x) * mean(theta_i) - (length(x) - 1) * theta_hat

#Results
theta_jack

```

Note for the equation ( which is theta-hat) the equation is as follows:

$$
\hat{\theta}jack= n\hat{\theta}-(n-1)\bar{\theta}_{(-)}
$$

## Question 2: Example 5.4.9

Part A

```{r}

mu_hat <- mean(Boston$medv)
mu_hat
```

Part B

```{r}
n <- length(Boston$medv)
se_formula <- sd(Boston$medv) / sqrt(n)
se_formula
```

Part C

```{r}
set.seed(1)

B <- 2000
boot_means <- numeric(B)

for (b in 1:B) {
  sample_b <- sample(Boston$medv, size = n, replace = TRUE)
  boot_means[b] <- mean(sample_b)
}

se_boot <- sd(boot_means)
se_boot
```

Both calculations are similar in response. The small difference represent sampling variability

Part D

```{r}

ci_boot <- c(mu_hat - 2*se_boot, mu_hat + 2*se_boot)
ci_boot

t.test(Boston$medv)
```

Part E

```{r}
M_hat <- median(Boston$medv)
M_hat

```

Part F

```{r}
set.seed(1)

boot_medians <- numeric(B)

for (b in 1:B) {
  sample_b <- sample(Boston$medv, size = n, replace = TRUE)
  boot_medians[b] <- median(sample_b)
}

se_median_boot <- sd(boot_medians)
se_median_boot
```
